The complex structure and peculiar internal motions of the planetary nebula NGC 6210

### 2020-06-18 ms.tex
Finish the conclusions!

\begin{figure}
  \includegraphics[width=\linewidth]
  {figs/turtle-flow-axis-history}
  \caption{
    Ejection history of each flow axis,
    assuming no acceleration or deceleration of the features.
    Lower-case roman numerals indicate sub-axes of axis~E.
    Uncertainties are typically of order \(\pm 30\%\),
    see Table~\ref{tab:3d} for details,
    except for \AxM{E}(ii) where the uncertainty is much higher.
  }
  \label{fig:axis-history}
\end{figure}

@@

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]
  {figs/turtle-flow-axis-history}
  \caption{
    Ejection history of each flow axis,
    assuming no acceleration or deceleration of the features.
    Lower-case roman numerals indicate sub-axes of axis~E.
    Uncertainties are typically of order \(\pm 30\%\),
    see Table~\ref{tab:3d} for details,
    except for \AxP{E}(ii) where the uncertainty is much higher.
  }
  \label{fig:axis-history}
\end{figure}

@@

The final axis, E, is the ejection axis of the low-ionization knot complexes,
which dominate the appearance of the nebula in the \nii{} line.
Axis~E is highly inclined (\(\approx\ang{70}\)) to the plane of the sky
and the low-ionization outflow is less well collimated than the lobes.
These combine to make the axis hard to identify in images,
although it is clearly revealed in the longslit spectra.
Furthermore, while A, B, C, and D are symmetry axes,
axis~E would be better described as an \emph{asymmetry} axis,
since the kinematic timescales are utterly different between the redshifted and blueshifted sides.
The red semi-axis (predominantly N and W of the central star)
was active with outflow velocities of \SI{30}{km.s^{-1}}
from \num{8000} to \SI{4000}{yr} ago,
that is, before the planetary nebula phase.
In contrast, the blue semi-axis (predominantly S and E)
was active with outflow velocities of \SI{50}{km.s^{-1}}
from \num{1200} to \SI{2700}{yr} ago,
making it the kinematically youngest component of the nebula.
The density of the low-ionization knots is too high for them to be explained by shocked ionized halo material,
so we propose that they represent a dense massive outflow from the central star system.
Their total mass is \SI{0.06}{\msun}, or about 30\% of the mass of the nebular shells.

NGC~6210 is the product of a relatively low-mass \(\approx \SI{1.25}{\msun}\) progenitor
and its post-AGB central star is halfway along its high-luminosity heating track.
In some ways it is very similar to much simpler nebulae such as NGC~1535 and IC~3568,
but its rich variety of bipolar and monopolar outflows,
combined with marked asymmetries in the nebular shells,
set it apart from most other nebulae.
An interacting triple star system is a natural explanation for the Turtle's many peculiarities,
but the exact mechanism is unknown
and direct evidence for multiplicity of the central star is still lacking.
We hope that our detailed elucidation of the Turtle's complicated history of anisotropic mass loss will provide inspiration for future modeling efforts.
